
## Code for calculating SEMs at each scale
# Since we are not able to work with more than one composite variable, 
# we build 3 models: one without composites (to adjust the basic model),
# one with a composite for the Climate -> RRich relationship and
# another with a composite for the Climate -> LRich relationship.
# The models with composite variables correspond to the block fit1 and fit2
# in the SEM code.
``` {r, tidy=T}
library(lavaan)
library(dplyr)
library(semPlot)

#load data
load("/Users/marialeomontes/Documents/BIOLOGIA/ARTICULOS/Local_Regional/Datos/loc.bas.Rdata")
loc.bas.indra <- loc.bas

#save all r2
r2 <- c(0,0,0,0,0,0,0,0)
# Scale 1 ####
#model fit
bd <- loc.bas.indra[[1]]
bdscaled <- scale(bd[3:9])
richSEM1 <- '
  #measurement model

  #opcion variable compuesta 1 (fit1)
  climR <~ 1*pa +pcq + tcqm + tam
  regrich ~ climR
  locrich ~ tcqm
  locrich ~ tam

  #opcion variable compuesta 2 (fit2)
  # climL <~ tcqm + 1*tam
  # locrich ~ climL
  # regrich ~ tam
  # regrich ~ tcqm
  # regrich ~ pa
  # regrich ~ pcq
  
  #regresiones
  locrich ~ regrich
  
  #correlations
  tam ~~ pa
  tam ~~ tcqm
  tam ~~ pcq
  pa ~~ tcqm
  pa ~~ pcq
  pcq ~~ tcqm
  
'

fit1 <- sem(model = richSEM1, data = bdscaled, fixed.x = FALSE, std.lv= T)
summary(fit1, standardized=TRUE)

# show coefficients
coef(fit1)

#show R-squared
r2[1] <- inspect(fit1, 'r2')

#show modification indexes
mod_ind1 <- modindices(fit1)
# 10 greatest modind
head(mod_ind1[order(mod_ind1$mi, decreasing=TRUE), ], 10)

#plot SEM
semPaths(fit1, layout="tree2",what="std")
 
# Scale 2 ####

bd <- loc.bas.indra[[2]]
bdscaled <- scale(bd[3:9])
richSEM2 <- '
  #measurement model

  #opcion variable compuesta 1 (fit1)
  climR <~ 1*pa +pcq + tcqm + tam
  regrich ~ climR
  locrich ~ tcqm
  locrich ~ tam

  #opcion variable compuesta 2 (fit2)
  # climL <~ tcqm + 1*tam
  # locrich ~ climL
  # regrich ~ tam
  # regrich ~ tcqm
  # regrich ~ pa
  # regrich ~ pcq
  
  #regresiones
  locrich ~ regrich

  #correlations
  tam ~~ pa
  tam ~~ tcqm
  tam ~~ pcq
  pa ~~ tcqm
  pa ~~ pcq
  pcq ~~ tcqm

'

fit2 <- sem(richSEM2, data=bdscaled, fixed.x=FALSE)
summary(fit2, standardized=TRUE)

# show coefficients
coef(fit2)

#show R-squared
r2[2] <- inspect(fit2, 'r2')

#show modification indexes
mod_ind <- modindices(fit2)
# 10 greatest modind
head(mod_ind2[order(mod_ind2$mi, decreasing=TRUE), ], 10)

#plot SEM
semPaths(fit2, layout="tree2",what="std")
 
# Scale 3####

bd <- loc.bas.indra[[3]]
bdscaled <- scale(bd[3:9])
richSEM3 <- '
  #measurement model

  #opcion variable compuesta 1 (fit1)
  climR <~ 1*pa +pcq + tcqm + tam
  regrich ~ climR
  locrich ~ tcqm
  locrich ~ tam

  #opcion variable compuesta 2 (fit2)
#   climL <~ 1*tcqm + tam
#   locrich ~ climL
#   regrich ~ tam
#   regrich ~ tcqm
#   regrich ~ pa
#   regrich ~ pcq
   
  #regresiones
  locrich ~ regrich

  #correlations
  tam ~~ pa
  tam ~~ tcqm
  tam ~~ pcq
  pa ~~ tcqm
  pa ~~ pcq
  pcq ~~ tcqm

'

fit3 <- sem(richSEM3, data=bdscaled, fixed.x=FALSE)
summary(fit3, standardized=TRUE)

# show coefficients
coef(fit3)

#show R-squared
r2[3] <- inspect(fit3, 'r2')

#show modification indexes
mod_ind3 <- modindices(fit3)
# 10 greatest modind
head(mod_ind3[order(mod_ind3$mi, decreasing=TRUE), ], 10)

#plot SEM
semPaths(fit3, layout="tree2",what="std")
 
# Scale 4 ####

bd <- loc.bas.indra[[4]]
bdscaled <- scale(bd[3:9])
richSEM4 <- '
  #measurement model

  #opcion variable compuesta 1 (fit1)
#   climR <~ 1*pa +pcq + tcqm + tam
#   regrich ~ climR
#   locrich ~ tcqm
#   locrich ~ tam

  #opcion variable compuesta 2 (fit2)
  climL <~ 1*tcqm + tam
  locrich ~ climL
  regrich ~ tam
  regrich ~ tcqm
  regrich ~ pa
  regrich ~ pcq
   
  #regresiones
  locrich ~ regrich

  #correlations
  tam ~~ pa
  tam ~~ tcqm
  tam ~~ pcq
  pa ~~ tcqm
  pa ~~ pcq
  pcq ~~ tcqm

'

fit4 <- sem(richSEM4, data=bdscaled, fixed.x=FALSE)
summary(fit4, standardized=TRUE)

# show coefficients
coef(fit4)

#show R-squared
r2[4] <- inspect(fit4, 'r2')

#show modification indexes
mod_ind <- modindices(fit)
# 10 greatest modind
head(mod_ind[order(mod_ind$mi, decreasing=TRUE), ], 10)

#plot SEM
semPaths(fit, layout="tree2",what="std")
 
# Scale 5 ####

bd <- loc.bas.indra[[5]]
bdscaled <- scale(bd[3:9])
richSEM5 <- '
  #measurement model

    #opcion variable compuesta 1 (fit1)
  climR <~ 1*pa +pcq + tcqm + tam
  regrich ~ climR
  locrich ~ tcqm
  locrich ~ tam

  #opcion variable compuesta 2 (fit2)
#   climL <~ 1*tcqm + tam
#   locrich ~ climL
#   regrich ~ tam
#   regrich ~ tcqm
#   regrich ~ pa
#   regrich ~ pcq
   
  #regresiones
  locrich ~ regrich


  #correlations
  tam ~~ pa
  tam ~~ tcqm
  tam ~~ pcq
  pa ~~ tcqm
  pa ~~ pcq
  pcq ~~ tcqm

'

fit5 <- sem(richSEM5, data=bdscaled, fixed.x=FALSE)
summary(fit5, standardized=TRUE)

# show coefficients
coef(fit5)

#show R-squared
r2[5] <- inspect(fit5, 'r2')

#show modification indexes
mod_ind5 <- modindices(fit5)
# 10 greatest modind
head(mod_ind5[order(mod_ind5$mi, decreasing=TRUE), ], 10)

#plot SEM
semPaths(fit5, layout="tree2",what="std")

# Scale 6####
bd <- loc.bas.indra[[6]]
bdscaled <- scale(bd[3:9])
richSEM6 <- '
  #measurement model

  #opcion variable compuesta 1 (fit1)
  climR <~ 1*pa +pcq + tcqm + tam
  regrich ~ climR
  locrich ~ tcqm
  locrich ~ tam

  #opcion variable compuesta 2 (fit2)
#   climL <~ 1*tcqm + tam
#   locrich ~ climL
#   regrich ~ tam
#   regrich ~ tcqm
#   regrich ~ pa
#   regrich ~ pcq
   
  #regresiones
  locrich ~ regrich

  #correlations
  tam ~~ pa
  tam ~~ tcqm
  tam ~~ pcq
  pa ~~ tcqm
  pa ~~ pcq
  pcq ~~ tcqm

'

fit6 <- sem(richSEM6, data=bdscaled, fixed.x=FALSE)
summary(fit6, standardized=TRUE)

# show coefficients
coef(fit6)

#show R-squared
r2[6] <- inspect(fit6, 'r2')

#show modification indexes
mod_ind <- modindices(fit6)
# 10 greatest modind
head(mod_ind[order(mod_ind$mi, decreasing=TRUE), ], 10)

#plot SEM
semPaths(fit6, layout="tree2",what="std")
 
# Scale 7####

bd <- loc.bas.indra[[7]]
bdscaled <- scale(bd[3:9])
richSEM7 <- '
  #measurement model

  #opcion variable compuesta 1 (fit1)
#   climR <~ 1*pa +pcq + tcqm + tam
#   regrich ~ climR
#   locrich ~ tcqm
#   locrich ~ tam

  #opcion variable compuesta 2 (fit2)
  climL <~ 1*tcqm + tam
  locrich ~ climL
  regrich ~ tam
  regrich ~ tcqm
  regrich ~ pa
  regrich ~ pcq
 
 #regresiones
  locrich ~ regrich
   
  #correlations
  tam ~~ pa
  tam ~~ tcqm
  tam ~~ pcq
  pa ~~ tcqm
  pa ~~ pcq
  pcq ~~ tcqm

'

fit7 <- sem(richSEM7, data=bdscaled, fixed.x=FALSE)
summary(fit7, standardized=TRUE)

# show coefficients
coef(fit7)

#show R-squared
r2[7] <- inspect(fit7, 'r2')

#show modification indexes
mod_ind <- modindices(fit7)
# 10 greatest modind
head(mod_ind[order(mod_ind$mi, decreasing=TRUE), ], 10)

#plot SEM
semPaths(fit7, layout="tree2",what="std")
 
# Scale 8####

bd <- loc.bas.indra[[8]]
bdscaled <- scale(bd[3:9])
richSEM8 <- '
#measurement model
 
 #opcion variable compuesta 1 (fit1)
  climR <~ 1*pa +pcq + tcqm + tam
  regrich ~ climR
  locrich ~ tcqm
  locrich ~ tam

  #opcion variable compuesta 2 (fit2)
#   climL <~ 1*tcqm + tam
#   locrich ~ climL
#   regrich ~ tam
#   regrich ~ tcqm
#   regrich ~ pa
#   regrich ~ pcq

  #regresiones
  locrich ~ regrich

  #correlations
  tam ~~ pa
  tam ~~ tcqm
  tam ~~ pcq
  pa ~~ tcqm
  pa ~~ pcq
  pcq ~~ tcqm

'

fit8 <- sem(richSEM8, data=bdscaled, fixed.x=FALSE)
summary(fit8, standardized=TRUE)

# show coefficients
coef(fit8)

#show R-squared
r2[8] <- inspect(fit8, 'r2')

#show modification indexes
mod_ind <- modindices(fit8)
# 10 greatest modind
head(mod_ind[order(mod_ind$mi, decreasing=TRUE), ], 10)

#plot SEM
semPaths(fit8, layout="tree2",what="std")

```

## Plots
```{r, tidy=T}
res <- read.csv("/Users/marialeomontes/Documents/BIOLOGIA/ARTICULOS/Local_Regional/Results/Results_SEMbasins.csv", header=T, sep=";", row.names = 1)

par(mfrow=c(1,2),mar=c(2,3,1,2), oma=c(0,0,0,0))
plot(x=c(1:8), y=res$climRr, main="SEM path values", type = "o", col="black", ylim=c(-1.4,0.5), xlab="Scale")
lines(x=c(1:8), y=res$climLr, type="o", col="red")
lines(x=c(1:8), y=res$RrLr, type="o", col="blue")
legend("bottomright", legend= c("Clim -> Rrich", "Clim -> Lrich", "Rrich -> Lrich"), col=c("black", "red", "blue"),lty=1:2, cex = 0.8)

plot(x=c(1:8), y=res$r2Rr, main="R2", type = "o", col="black", ylim=c(0,1), xlab="Scale")
lines(x=c(1:8), y=res$r2Lr, type="o", col="red")
legend("topright", legend= c("R2 Rrich", "R2 Lrich"), col=c("black", "red"),lty=1:2, cex = 0.8)

